\section{Conclusion and Future works}
\subsection{Results}
The L-impiccato2.0 project has achieved the goal of creating an educational, inclusive and technologically advanced application that reinterprets a classic game with the potential offered by multimodal interaction. The most significant results obtained are:
\begin{itemize}
    \item Creation of a working application, entirely written in Python, multiplatform and modular.
    \item  Integration of voice and gesture inputs, with robust letter recognition via speech\_recognition and CNN on webcam images.
    \item Design of a responsive graphical interface, simple to use and consistent with usability principles.
    \item Implementation of a state manager and an OpenAI agent, able to dynamically manage the context, interpret commands in natural language and orchestrate the interaction between components.
    \item In-depth testing, which demonstrated the reliability of the system under real conditions and the satisfaction of the users involved.
\end{itemize}

From an educational point of view, the project represented a complete software design experience, from the study of requirements to the realisation of a working intelligent system.

\subsection{Future Goals}
The project has a wide scope for further development. Future developments considered include:
\begin{itemize}
    \item Expansion of vocabulary and support for more languages, including for international educational contexts.
    \item Addition of a speech synthesis module, to provide fully vocal responses and feedback (text-to-speech).
    \item Improved CNN for gesture recognition, with larger datasets and advanced data augmentation techniques.
    \item Multiplayer or cooperative mode, with support for multiple users or timed challenges.
    \item Integrated onboarding/guidance system, to assist the user in initial interactions (voice/visual tutorial).
    \item Save user profile and match history to help track progress.
    \item Deploy on web or mobile, using frameworks such as Streamlit, Flask or React Native.
\end{itemize}


